---
output: github_document
---

https://httr.r-lib.org/articles/quickstart.html

```{r}
library(httr)
r <- GET("http://httpbin.org/get")
```

```{r}
r
```

会告诉什多大`Size: 325 B`

```{r}
headers(r)
```

`GET()` is used by your browser when requesting a page, and `POST()` is (usually) used when submitting a form to a server. `PUT()`, `PATCH()` and `DELETE()` are used most often by web APIs.

# status

>
The data sent back from the server consists of three parts: the status line, the headers and the body.
>
The status code is a three digit number that summarises whether or not the request was successful (as defined by the server that you’re talking to). 
>
A successful request always returns a status of 200.
>
Common errors are 404 (file not found) and 403 (permission denied).

```{r}
http_status(r)
```

```{r}
status_code(r)
```

# text

```{r}
content(r, "text")
```

```{r}
content(r, "text", encoding = stringi::stri_enc_detect(content(r, "raw")))
```

`stringi::stri_enc_detect(content(r, "raw"))`自动查询 Encoding

List化

```{r}
content(r, "parsed")
```

```{r}
library(tidyverse)
content(r, "parsed") %>% 
    str()
```

# headers

```{r}
headers(r)
```

>
http headers are case insensitive

```{r}
headers(r)$date
headers(r)$DATE
```

# cookies

```{r}
r <- GET("http://httpbin.org/cookies/set", query = list(a = 1))
cookies(r)
```

```{r}
r <- GET("http://httpbin.org/cookies/set", query = list(b = 1))
cookies(r)
```

```{r}
r <- GET("http://httpbin.org/cookies/set", query = list(c = 1))
cookies(r)
```

这样产生三个参数。

the request 和 the response 的区别

类似与 responsse

```{r}
r <- GET("http://httpbin.org/get", 
  query = list(key1 = "value1", key2 = "value2")
)
content(r)$args
```

```{r}
r <- GET("http://httpbin.org/get", 
  query = list(key1 = "value 1", "key 2" = "value2", key2 = NULL))
content(r)$args
```

`NULL`的 key-value pairs 会自动去掉。

```{r}
r <- GET("http://httpbin.org/get", add_headers(Name = "Hadley"))
str(content(r)$headers)
```

注意，
`Name = "Hadley"`并不存在于`http://httpbin.org/get`的headers中。

>
Cookies are simple key-value pairs like the query string, but they persist across multiple requests in a session (because they’re sent back and forth every time). 

```{r}
r <- GET("http://httpbin.org/cookies", set_cookies("MeWant" = "cookies"))
content(r)$cookies
```

>
Note that this response includes the `a` and `b` cookies that were added by the server earlier.

```{r}
r <- POST("http://httpbin.org/post", body = list(a = 1, b = 2, c = 3))
r
```

```{r}
url <- "http://httpbin.org/post"
body <- list(a = 1, b = 2, c = 3)

# Form encoded
r <- POST(url, body = body, encode = "form")
# Multipart encoded
r <- POST(url, body = body, encode = "multipart")
# JSON encoded
r <- POST(url, body = body, encode = "json")
```


```{r eval=F}
POST(url, body = body, encode = "multipart", verbose()) # the default
POST(url, body = body, encode = "form", verbose())
POST(url, body = body, encode = "json", verbose())
```

开始讲 POST 请求
以上`verbose()`是动态的，所以只能在console完成。

```{r}
POST(url, body = upload_file("mypath.txt"))
POST(url, body = list(x = upload_file("mypath.txt")))
```

`"data": "This is a upload txt."`

```
  "files": {
    "x": "This is a upload txt."
  }, 
```

这个是安装的内容。

不是特别清楚，POST请求，add headers 和 data 等的区别。
直接看案例。

这是看爬虫方面内容，最bug的地方。